\documentclass[english]{tktltiki}
%\documentclass[a4paper]{article}
%\usepackage[utf8]{inputenc}
\usepackage[pdftex]{graphicx}
\usepackage{subfigure}
\usepackage{alltt}
\usepackage{gensymb} % for \textdegree
% break on long hyphens to prevent overstepping bounds
%\usepackage[hyphenbreaks]{breakurl} 
%\usepackage[hyphens]{url}
% to force 1-in margins
%\usepackage[margin=1in]{geometry}


%%% Source for figures for my safety
\newcommand*{\captionsource}[2]{%
	\caption[{#1}]{%
		#1%
%		\\\hspace{\linewidth}%
%		\textbf{Source:} #2%
	}%
}
%%%


\begin{document}
%\doublespacing
%\singlespacing
%\onehalfspacing

\title{Machine Learning Strategies in Cribbage}
\author{Sean R. Lang}
\date{\today}

\maketitle

\numberofpagesinformation{\numberofpages\ pages + \numberofappendixpages\ appendices}
\classification{\protect{\ \\
		%A.1 [Introductory and Survey],\\
		%H.5.1 [Artificial, augmented, and virtual realities],\\
		%I.3.7 [Virtual Reality]
	}
}

\keywords{machine learning, cribbage}

\begin{abstract}
\input{sections/abstract.sec.tex}
\end{abstract}

%\mytableofcontents

\section{Introduction}
\input{sections/intro.sec.tex}

%%%
I just want to see if unicode characters will appear.
Jag måste se om unicode-characterer funger.
minä haluan katsoa kirjain öööö.
%%%

%%%
Generic introductory stuff giving a sentence or probably a paragraph about
each of the sections covered.
%%%


\section{Literature Review}
\input{sections/literature.sec.tex}

%%%
Overview of the current literature surrounding this topic.
%%%

\begin{itemize}
	\item Research done in cribbage
	\item Research done in related imperfect information games (e.g. poker)
	\item Overview on expert witness machine learning
	\item Any other topic that ends up getting used (Bayesian logic, statistics?)
\end{itemize}


\section{Data and Methods}
\input{sections/data_methods.sec.tex}

%%%
Walk-through of how I went about researching the topic.
%
(Maybe I should keep a diary or log or something so this isn't half made up
at the end.)
%
When all is said and done, include the final ``output'' graph in some easily
viewable format (121-by-121 table of miniature bar graphs, RGB combination in
each cell?).
%%%

\begin{itemize}
	\item Creation of framework
	\item Creation of ``expert advisor''
	\item Training method for listener/combiner
	\item Initializations for training
\end{itemize}


\section{Findings}
\input{sections/findings.sec.tex}

%%%
What are the final results of the ``experiment.''
%%%

\begin{itemize}
	\item Where did each initialization family end up going?
	\item Were they different or did the agent learn a ``single'' strategy
		in general?
	\item All this and more will be answered \ldots after the break!
\end{itemize}


\section{Discussion}
\input{sections/discussion.sec.tex}

%%%
This is the difficult part.
%
What does this part mean?
%
And how does it differ from what I've already covered above in the Findings
section.
%%%


\section{Conclusion}
\input{sections/conclusion.sec.tex}

%%%
Generic closing remarks and rephrasing of the original introduction again
in parting.
%
Because this is a thesis and likely fairly long, ``In section X, we covered Y''
is probably allowed and not tacky.
%%%

%\newpage

\nocite{*}
\bibliographystyle{tktl}
\bibliography{references}

%\lastpage

%\appendices

% TODO: a good appendix would be the rules to cribbage
%	Question: am I allowed to copy-paste the rules from cribbage.org (cited)

%\pagestyle{empty}

\end{document}


