\subsection{Reinforcement Learning}
\label{sec:intro-reinf}

%%%
% Background of topics in reinforcement learning
%%%

%%%
% What is Reinforcement Learning:
% When is it used:
%%%

%%%
Reinforcement learning is the machine learning equivalent of learning from one's
failures,
rather than being coached to the correct answer.%
\footnote{
	Unless otherwise specified,
	all information presented in this section is referenced from
	Sutton and Barto~\cite{rl_book}.
}
%
In classical machine learning methodologies,
the agent discovers an optimum model for a problem by approximation methods
centered around minimizing a set loss function over a given set of data
while assuming a known model for the solution.
% ^^^ TODO: check if accurate enough to say
%
In reinforcement learning,
however,
the agent finds the optimal solution to the problem by repeatedly taking an
action in an environment and gaining a reward or punishment for each
action taken.
%
It is the same principle used in teaching a pet or animal to do a trick:
offer a full or partial reward for successful completion of the trick or
for progress in the correct direction.
%
As a comparison to teaching a human how to add,
the strategy used in classical machine learning would be what is used in
classrooms today:
teach the method of adding digits and handling carry-over,
giving some guidance and sample problems to ensure the technique is solidly
replicable.
%
Meanwhile, teaching a human how to add by reinforcement learning would
mean merely quizzing the subject by asking him to answer an addition problem
while giving a vague hint as to how right or wrong they were.
%
After enough rounds of this,
the student will eventually figure out his own method for adding two numbers
with the same accuracy as an established method.
%%%

%%%
While this may seem like a silly example where classical methods would clearly
be the superior method,
where reinforcement learning comes into its own is in situations in which no
known answer exists for a problem.
%
Take for instance the problem of learning chess.
%
In humans
basic strategies for how to handle certain situations can be taught,
but these are all from one's own or others' prior experience,
and while they may bolster knowledge on heretofore unknown situations,
they cannot possibly cover all possible chessboard layouts.
%
The best way to learn, in humans and computers, is by doing.
%
Barring savants such as Bobby Fischer,
humans will learn how to play chess better by playing games against varying
opponents.
%
After a game has been played,
the player can see what worked and failed during the game to cause the win or
loss and extrapolate what to do if a similar situation occurs.
%
Classical teaching methodologies would not be highly applicable in this
situation because there is no single correct strategy in chess that can
be taught.
%%%

%%%
% Loss functions in 'classical' machine learning
%	and how they are unusable in reinforcement learning scenarios
%	What is a reinf learning scenario?
%		when is it used/favored
%%%

\input{sections/intro/reinf/background.sub.sub.sec.tex}

\input{sections/intro/reinf/learning.sub.sub.sec.tex}
