
\subsubsection*{Learning Rate Adjustment}
\label{sec:findings-expts-learnrate}

%%%
In order to determine if the learning rate was too high in Round 2,
even though it had been significantly reduced from Round 1,
a varying amount of learning rates were tried.
%
These runs were intended to see if an optimal policy was being overstepped by
making too large of an adjustment.
%%%


\paragraph*{Results}

%%%
% TODO: verify results when experiment has been rerun
% and choose correct set of answers
%%%

%%%
% 2 possibilities foreseeable for results:
%	1. patterns are the same
%	2. something new is learned
%%%


%%%
As can be seen in Figure~\{ref{expts-lr-comp},
the same set of behavioral patterns are learned as in previous training
sessions.\footnote{
	As with the decay section,
	this part needs to be rerun,
	so accuracy will need to be verified.
	% TODO: remove footnote
	What's more: since this section is speculative,
	only one of either this paragraph or the next one will actually be used.
}
%
Therefore,
it is safe to speculate that some optimum is not being stepped over,
allowing a worse set of weights to be pursued instead.
%
Thus,
the agent is correctly learning to solve the problem.
%
Ergo,
the problem setup itself or else the system of rewards
must be flawed in some manner.
% TODO: ^ if this is the case, consider opening the sanitycheck section with
% a pointing out of this
%
However,
a decrease in scaling factor leads to slower adjustments,
showing that the scaling factor does indeed function as a learning rate.
%%%

%%%
% TODO: ^ or v: choose one
%%%

%%%
As can be seen in Figure~\{ref{expts-lr-comp},
a different set of behavioral patterns are learned when the
scaling factor,
i.e. the learning rate,
is lowered to \${VALUE}. % TODO: <-- value
%
This serves to show that a better policy was previously being skipped over
by previous training sessions.
%
Were time to permit,
this new learning rate would be further trained to find a more optimal
policy.
%
Alas, this is no longer an option,
so the results of such an inquiry are left for speculation
or for future research.
% TODO: ^ if this is the case, probably include in discussion section
%%%

% fig:expts-lr-comp
\input{sections/findings/experiments/learning_rate/comparison.fig.tex}

