
\subsection{Strategies}
\label{sec:dm-methods-strategies}

%%%
% Information which strategies were created and how they basically operated
%	side note about the need to create a different script
%%%

%%%
%During the simulation of games,
A few basic behavioral strategies were coded for the agent to learn
over the course of multiple simulated games.
%
These represented most of the basic factors which a player will consider when
making their decision as to which cards to keep.
%
These included:
\begin{itemize}
\item \texttt{hand\_max\_min}:
	%
	The hand(s) which has the maximum minimum possible score for the kept cards
	will be more highly desired.
	%
	This is equivalent to choosing the hand with the largest guaranteed points.
	%
\item \texttt{hand\_max\_avg}:
	%
	The hand(s) with the maximum average points over all possible cut cards will
	be the most highly desired.
	%
	This strategy is useful for trying to maximize the expected score of one's
	own hand.
	%
\item \texttt{hand\_max\_med}:
	%
	The hand(s) with the maximum median points possible to score will be the most
	highly desired.
	%
	Similar to \texttt{hand\_max\_avg}, this strategy is useful when trying to
	maximize one's hand's expected score.
	%
\item \texttt{hand\_max\_poss}:
	%
	The hand(s) with the maximum possible score will be the most highly desired.
	%
	This strategy can be thought of as Hail Mary choice for the player trying to
	score as many points as possible, not taking into account its unlikelihood.
	%
\item \texttt{crib\_min\_avg}:
	%
	The hand(s) with the minimum average amount of points scored in the crib is
	the most highly desired.
	%
	This strategy would be a very defensive strategy typically used by the pone
	to avoid giving points to the dealer.
	%
\item \texttt{pegging\_max\_avg\_gained}:
	%
	The hand(s) with the maximum average points gained through pegging is the most
	highly desired.
	%
	This strategy would be useful for end-game play in a tight game.
	%
	For instance, if both players are close to winning, the dealer may
	choose to forego placing points into their hand and instead try to
		``peg out''
	since it is unlikely that they will get a chance to count their hand at all.
	%
\item \texttt{pegging\_max\_med\_gained}:
	%
	The hand(s) with the maximum median points scored during play will be the most
	highly desired.
	%
	This strategy is similar to \texttt{pegging\_max\_avg\_gained} in its use,
	but uses a slightly different internal measure for ranking.
	% TODO: ^ better explanation
	%
\item \texttt{pegging\_min\_avg\_given}:
	%
	The hand(s) with the minimum average points scored by the opposing player
	will be the most highly desired.
	%
	This is a very defensive strategy also useful at the end of the game to
	prevent the opposing player from pegging out.
	%
\end{itemize}
%
The above definitions refer to a hand's desirability.
%
This can be thought of as an internal ranking of how likely a given strategy
would be willing to choose a particular combination of cards.
%
This desirability score is then scaled to to lie in the range $[0, 1]$ with
$1$ representing the best possibilities.
%
This scaling allows for possibilities which are ``almost as good'' to not be
ignored in later weighting stages.
%Because there are likely to be multiple possible combinations of cards which
%have the same desirability according to any given strategy,
%the implementation of the each strategy will point out all such possibilities.
%%%


%%%%
%The choosing mechanism will then apply a different weight to each strategy's
%picks based on that strategy's weighting for the given score time.
%% TODO: ^ word above better                             ^^^^^^^^^
%%
%In this way, a hand that was highly recommended by strategies which are highly
%trusted will be more likely to be picked.
%%
%Multiple recommendations from multiple strategies will also be combined together
%to further boost popular suggestions.
%%
%After all recommendations have been accumulated,
%the option with the highest weight will be chosen by the agent for play in that
%round.
%%
%In the event of a tie between two or more combinations of cards,
%the combination which was recommended by the
%% TODO: ^ tie-breaking mechanism
%%%%


%\subsubsubsection*{Database Population}
%%%
Because of the massive amount of possible combinations%
% TODO: vvv many || all?
\textemdash many of which were unique due to the cards' position affecting the
scoring outcome\textemdash%
the evaluation of some of these possibilities in which the crib was involved
in real-time took a handful of seconds to evaluate during development.
%
This was deemed much too slow as over the course of hundreds or thousands of
simulated games,
this delay would very quickly accumulate to performance-affecting delays.
%
As a result, an alternative strategy of pre-computing the required knowledge and
storing the values of interest into a database was implemented instead.
%%%

%%%
There are ${52 \choose 6}$ possible combinations of card which can be dealt to
either player.
%
Of these possibly dealt hands, there are then ${6 \choose 4} = 15$ possible
combinations of cards that can be kept and ``tossed'' to the crib.
%
For each of these $15$ possible there are a further $(52-6)=46$ possible cards
that must be considered as possible cut cards for the kept hand.
%
Additionally, for the thrown set of cards,
there are ${46 \choose 2} = 1035$ possible combinations of cards which can be
thrown by the opposing player into the crib as well as the
$(46-2)=44$ remaining possible cut cards.
%
These cut cards must be considered separately in such a manner of
evaluating ${46 \choose 2} \times 44 = 45540$ possibilities rather than
simply looking at each of ${46 \choose 3} = 15180$ possibilities because
whether or not the card is in the crib or not can affect the score.%
\footnote{
	For example, as per the right-jack rule,
	a hand of 5\clubs\ 5\hearts\ 5\spades\ J\diamonds\ 
	with a cut card of 5\diamonds\ is a perfect hand
	with a score of 29,
	but moving those cards around so that the jack is no longer in the hand
	and is instead the cut
	(i.e. hand of 5\clubs\ 5\hearts\ 5\spades\ 5\diamonds\
	with a cut of J\diamonds)
	yields a score of 28.
}
%
Just as crucially, there are small differences in scoring the crib as opposed to
scoring the player's own hand that mean that previous evaluations results are
not reusable.
%
For instance, the rule for gaining points from a flush are more lenient for
one's own hand than for the crib:
the crib's flush must be a five-card flush containing the cut card
whereas the player's own hand needs only be a four-card flush of their own
hand with bonus points gained from the crib also matching.
%
This means that, altogether, there are 
\[
	{52 \choose 6}
	{6 \choose 4}
	\left(
		\left(46\right) +
		\left(
			{46 \choose 2} \times 44
		\right)
	\right)
	\approx
	1.3921 \times {10}^{13}
	% Google answer: 1.3920952e13
\]
possible combinations of cards that need to be evaluated in total to fully 
understand the statistics
of a cribbage game for each hand.
% TODO: wording of above needs to be better
%%%

%%%
% TODO: majority or rest? depends on status at end
Although the majority of this project was coded in Python for its ease of use
and speed of development,
due to the performance-crucial, basic mathematical operations involved,
the overheads of using a higher-level language was deemed too critical and
this particular tool was developed in C instead.
%
To put the performance gains into perspective,
at its fastest, most parallelly processed state,
the Python database populator was estimated to take approximately 4 months to
simply list and evaluate all possible scores on a development machine,
disregarding the file I/O operations required to write the results to the
database.
%
The same functionality, with the addition of file I/O,
in the C program would take a relatively mere 14 days
on that same machine.
%
Thankfully, most of the framework for this rewrite had actually been developed
previously as part of a mental exercise, so the loss in time for the rewrite was
minimal and well worth the time saved in execution.
%
Furthermore, access to a high-performance server allowed for futher
paralellization which cut the final run time down to approximately 5 and a half
days.
%%%

%%%
Careful consideration and preparation needed to be taken
for the retrieval of this information, however.
%
The trillions of combinations could not be quickly searched by card value as
doing so would search the entirety of the database on each lookup,
decreasing the performance so much as to be worse than simply
enumerating the combinations on-demand.
%
A rather simple solution to this problem was to search by index
instead of by card comparison.
%
These indices could not simply be stored in the memory of the running program
because the sheer size required to store all of the indices at all times
would rival that of the database,
and its population would take considerable enough time.
%
Thus, a quick and reliable method for creating and recreating these keys
needed to be used.
%
As the cards were represented internally as an integer between $0$ and $51$
(inclusive)
and there were only 6 cards for indexing,
the concatenation of the cards' digits in (keep,toss) order
would create a number with at most twelve digits,
with an absolute maximum value of 484950514647,
well within the range of numbers addressable by an integer.\footnote{
	Thanks to implementation,
	the order of cards was guaranteed to be sorted within each tuple,
	so each combination of cards was tracked and not permutation.
	% TODO: better phrasing of this
	% TODO: need to change to not numbers
}
%
This index could be created by a very simple process of 6 multiplications and
5 additions
while still being guaranteeably unique.
%%%


%%%
% TODO: probably could use a different header here for this vvv
%%%


%%%
% TODO: need to write something about how the pegging was recorded
While the combinations of chosen and tossed scores could be evaluated before any
games had actually been played,
the hands' usefulness during the pegging portion of the round needed to be
evaluated in semi real-time.
%
%A single pegging agent was programmed with heuristics gained from %reading
%a cribbage strategy book.%
%\cite{cribbage_strategy_guide}
A single pegging agent was programmed with a simple one-ahead greedy heuristic:
the card that gained the most points when played next was selected with ties
broken by choosing the lower-valued card that reached that score.
% TODO: implementation change: choose the higher-valued card to potentially
%	avoid giving a go
%
This agent was then played against a copy of itself with randomly allocated
cards and the results of that round were recorded for each agent to provide an
initial knowledge base.
%
These results would then be queried by the agent during the choose phase of the
game and contributed to at the end of the pegging phase.
% TODO: define pegging and choosing phases
%%%

